Make manuscript figures

### 2021-10-29 scripts/R/make_manuscript_figures.rmd
squick model figure a bit

OU_plot <- ggplot(
      data = traceplot,
      aes(x = time, y = v, group = lineage, color = I(color))) +
      geom_line(size = 1.25) +
      labs(
        x = expression('Substitutions site'^-1 * ' year'^-1),
        y = expression(italic(g)[v])) +
      shared_theme +
      stat_function(fun = mu_OU, color = "black", linetype = "dashed")

@@

# Align OU and tree plots
left_side <- plot_grid(OU_plot, tree_plot, align = "v", axis = "lr", nrow = 2, rel_heights = c(2, 1), labels = c("A", "C"))
right_side <- plot_grid(NULL, e_plot, NULL, nrow = 3, rel_heights = c(1, 2, 1), labels = c("", "B", ""))

png(
      filename = paste(FIGDIR, "model_figure.png", sep = "/"),
      width = linewidth, height = height, units = "cm", res = 300)
      plot_grid(left_side, NULL, right_side, ncol = 3, rel_widths = c(1.5, 0.2, 1))
dev.off()

>>>>

OU_plot <- ggplot(
      data = traceplot,
      aes(x = time, y = v, group = lineage, color = I(color))) +
      geom_line(size = 1.25) +
      labs(
        x = element_blank(),
        y = expression(italic(g)[v])) +
      shared_theme +
      stat_function(fun = mu_OU, color = "black", linetype = "dashed")

@@

# Align OU and tree plots
left_side <- plot_grid(OU_plot, tree_plot, align = "v", axis = "lr", nrow = 2, rel_heights = c(3, 1), labels = c("A", "C"))
right_side <- plot_grid(NULL, e_plot, NULL, nrow = 3, rel_heights = c(1, 2, 1), labels = c("", "B", ""))

png(
      filename = paste(FIGDIR, "model_figure.png", sep = "/"),
      width = linewidth * 2/3, height = height * 2/3, units = "cm", res = 300)
      plot_grid(left_side, NULL, right_side, ncol = 3, rel_widths = c(1.5, 0.1, 1))
dev.off()
